Baseline centering problem

### 2019-01-12 paper/tangotd.tex

Building a universal policy. One may make the policy depend on a goal
representation $\omega$ as an additional input. One may simultaneously
compute $Z(s_1,s_2,\omega)$, namely the $Z$ function when following the
policy with goal $\omega$, and train at the same time a map $s_2\mapsto \omega=\Omega(s_2)$ and
policy parameters $\pi(a|s_1,\omega)$ such that following
$\pi(|\Omega(s_2))$ indeed goes towards $s_2$, namely, the policy
gradient for every $s_2$ is
\begin{equation}
\partial \pi(a|s,\Omega(s_2))\E_{s'|s,a} \E_{s_2\sim \rho} \,
(z(s',s_2,\Omega(s_2))-z(s,s_2,\Omega(s_2)))
\end{equation}
[TODO check this is indeed the policy gradient for the time spent at
$s_2$ if following policy $\pi(|\Omega(s_2))$]. Advantage: diversity of
policies should appear by itself, no need to manually force options to be
distinct. Depends on a chosen distribution of goals $s_2$; we could learn
to go to uniformly distributed states, or create a goal at points where
we observe a high reward value (so learning to go to all states with a
reward). Just fixing $\Omega(s)\deq s$ once and for all might work, in
principle, but may be ambitious. TODO check:
this is with a reward a Dirac at $s_2$, check there's no technical
problem wrt the reference distribution $\rho(s_2)$, as we use $z$ not $Z$
in the policy gradient and $z$ is the density of $Z$ wrt $\rho$ but I
think it's correct. Actually, for goal representations, a goal is not
necessarily a state itself, should be a feature of states, or some
representation of a reward function, so we should figure out the way to
give a meaning to $\Omega(R)$ for an arbitrary reward $R$. The
representation of $Z$ as $Z=\transp{\green}f$ does that automatically,
thanks to linearity wrt $R$.

>>>>

Building a universal policy. One may make the policy depend on a goal
representation $\omega$ as an additional input. One may simultaneously
compute $Z(s_1,s_2,\omega)$, namely the $Z$ function when following the
policy with goal $\omega$, and train at the same time a map $s_2\mapsto \omega=\Omega(s_2)$ and
policy parameters $\pi(a|s_1,\omega)$ such that following
$\pi(|\Omega(s_2))$ indeed goes towards $s_2$, namely, the policy
gradient for every $s_2$ is
\begin{equation}
\partial \pi(a|s,\Omega(s_2))\E_{s'|s,a} \E_{s_2\sim \rho} \,
(z(s',s_2,\Omega(s_2))-z(s,s_2,\Omega(s_2)))
\end{equation}
[TODO check this is indeed the policy gradient for the time spent at
$s_2$ if following policy $\pi(|\Omega(s_2))$]. Advantage: diversity of
policies should appear by itself, no need to manually force options to be
distinct. Depends on a chosen distribution of goals $s_2$; we could learn
to go to uniformly distributed states, or create a goal at points where
we observe a high reward value (so learning to go to all states with a
reward). Just fixing $\Omega(s)\deq s$ once and for all might work, in
principle, but may be ambitious (or use a summary/auto-encoded value of
$s$). TODO check:
this is with a reward a Dirac at $s_2$, check there's no technical
problem wrt the reference distribution $\rho(s_2)$, as we use $z$ not $Z$
in the policy gradient and $z$ is the density of $Z$ wrt $\rho$ but I
think it's correct. Actually, for goal representations, a goal is not
necessarily a state itself, should be a feature of states, or some
representation of a reward function, so we should figure out the way to
give a meaning to $\Omega(R)$ for an arbitrary reward $R$. The
representation of $Z$ as $Z=\transp{\green}f$ does that automatically,
thanks to linearity wrt $R$. This could even help with exploration:
setting temporary goals towards already-seen past states solves the "pure
random walk" problem by introducing temporary momentum; one can even
increase temperature a bit on $\omega$, by using slightly larger/more
variant values of $\omega$ as the goal.
